---
site:
  output: html
  theme: quarto
---

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}
# Install and load the slickR package
# install.packages("slickR")
library(htmltools)
library(slickR)
library(bslib)
```

<style>

/* Style the cards */
  .card {
    box-shadow: 0 4px 8px 0 rgba(0, 0, 0, 0.2);
    max-width: 100%;
    margin: auto;
    text-align: center;
    font-family: arial;
    border-radius: 10px;
    box-shadow: 0 4px 8px 0 rgba(0, 0, 0, 0.2);
    overflow: hidden;
  }

  .title {
    color: grey90;
    font-size: 30px;
  }
  
  h1 {
    font-size: 30px;
    text-align: center;
  }


  a {
    text-decoration: none;
    font-size: 22px;
    color: white;
  }

  button:hover, a:hover {
    opacity: 0.7;
  }

_______________________________________________

  /* Style the carousel container */
  .carousel {
    width: 600px;
    margin: 0 auto;
    overflow: hidden;
    position: relative;
  }

  /* Style the carousel slides */
  .carousel-slide {
    display: flex;
    width: 100%;
    height: 300px;
  }

  .button-prev {
    left: 10px;
  }

  .button-next {
    right: 10px;
  }
</style>


```{r styling, echo=FALSE, message=FALSE, warning=FALSE}
# Add some custom CSS styling to the cards
tags$style("
  /* Style the card container */
  .card {
    box-shadow: 0px 4px 8px 0px;
    max-width: 100%;
    max-height: 100%;
    margin: auto;
    text-align: center;
    font-family: arial;
    border-radius: 10px;
    overflow: hidden;
  }

  /* Style the card header */
  .card-header {
    padding: 10px;
    background-color: black;
    color: white;
    text-align: center;
    font-family: arial;
    font-size: 30px;
    font-weight: bold;
  }

  /* Style the card image */
  .card-image {
    width: 100%;
    object-fit: cover;
    border-radius: 10px;
  }

  /* Style the card text */
  .card-text {
    color: grey90;
    font-size: 30px;
  }
  
  /* Style button*/
  button {
    border: none;
    outline: 0;
    display: inline-block;
    padding: 8px;
    color: white;
    background-color: #000;
    text-align: center;
    cursor: pointer;
    width: 100%;
    font-size: 30px;
    border-radius: 10px;
  }
  
  /* Container holding the image and the text */
  .container {
    position: relative;
    text-align: center;
    color: white;
    object-fit: fill;
    max-width: 100%;
    max-height: 100%;
    margin: auto;
  }

  /* Top left text */
  .top-left {
    position: absolute;
    max-top: 100px;
    max-left: 205px;
    max-right: 200px;
    min-bottom: 100px;
    color: grey90;
    font-size: 30px;
    background-color: grey;
  }
")
```



```{r landingpage, echo=FALSE}
# Create a vector of image URLs
images <- c(
  "/pages/images/image5.png"
)

# Create a vector of card texts
texts <- c(
  "Find places where your dollars go the farthest and tips to create amazing travel experiences without breaking the bank. Travel more and spend less!"
)

# Create a list of HTML tags for the cards
card(
  card_header(
    class = "card-header",
    "Canary ToursKE"
  ),
  
  card_body(
    # Add an img tag for the card image
    htmltools::tags$img(
      src = images,
      class = "card-image",
    )),
    
    card_body(
      # Add a div tag for the card text
      htmltools::tags$div(
        class = "card-text",
        texts
      )),
    
  card_body(
      htmltools::tags$button(
        class = "card-button",
        htmltools::tags$a(
          href = "https://chat.whatsapp.com/D6QKPzWip0HGCPf8P3Z5Yb",
          "Contact Us"
        )
      )
  )
)
```

________________________________________________________________________
# Our Mission

```{r mission, echo=FALSE}
# Create a vector of card texts
texts <- c(
  "Turning every moment into a lifetime memory"
)

# Create a list of HTML tags for the cards
card(
  card_body(
    # Add an img tag for the card image
    htmltools::tags$p(
      texts,
      class = "title"
    ))
)
```

_______________________________________________________________________
# Our Vision

```{r vision, echo=FALSE}
# Create a vector of card texts
texts <- c(
  "Taking adventure to another level"
)

# Create a list of HTML tags for the cards
card(
  card_body(
    # Add an img tag for the card image
    htmltools::tags$p(
      texts,
      class = "title"
    )),
  
  class = "card2" 
)
```

_______________________________________________________________________
:::{.grid}
::: {.g-col-12}
# Deals!

```{r, echo=FALSE}
# Create a vector of image URLs
images <- c(
  "/pages/images/image4.jpg",
  "/pages/images/image7.jpg",
  "/pages/images/image1.jpg",
  "/pages/images/image6.jpg"
)

# Create a vector of card headers
headers <- c("The thrill of a game drive with Canary ToursKE", "Other with Canary ToursKE", "Cultural adventures with Canary ToursKE", "Corporate Events with Canary ToursKE")

# Create a vector of card texts
texts <- c(
  "As the sun rises over the vast plains, game drive enthusiasts embark on their safari vehicles, accompanied by experienced guides and trackers. The open-sided 4x4 vehicles provide an unobstructed view of the surrounding landscapes, ensuring that every moment is captured, from the majestic elephants grazing in the distance to the elusive big cats prowling through the grass",
  
  " ",
  
  "Kenya, a diverse and vibrant country in East Africa, is home to a rich tapestry of cultural practices that reflect the traditions and values of its numerous ethnic groups. These practices, deeply rooted in history, play a significant role in shaping the identity of the Kenyan people.",
  
  " "
)

# Create a list of HTML tags for the cards
cards <- lapply(seq_along(images), function(i) {
  card(
  card_header(
    # Add an img tag for the card image
    class = "card-header",
    htmltools::tags$p(
      headers[i]
    )),
    
    card_body(
      # Add a div tag for the card text
      class = "card-image2",
      
      htmltools::tags$div(
        class = "container",
        htmltools::tags$image(
        src = images[i]
      )),
      
      htmltools::tags$div(
        class = "top-left",
        htmltools::tags$p(
        texts[i]
      ))
    )
  )
})

# Create a slick carousel with the cards
navset_card_tab(
  full_screen = FALSE,

  nav_panel(
    title = "Game drives",
    cards[1]
  ),
  nav_spacer(),
  
  nav_panel(
    title = "Other",
    cards[2]
  ),
  nav_spacer(),
  
  nav_panel(
    "Cultural Adventures",
    cards[3]
  ),
  nav_spacer(),
  
  nav_panel(
    "Corporate Activities",
    cards[4]
  )
)
```
:::
:::
